---
title: "cloudflarer cheatsheet"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{cloudflarer cheatsheet}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label: setup
#| include: false
library(cloudflarer)
Sys.setenv(CLOUDFLARE_API_TOKEN = "cloudflarer-vignette")
vcr::vcr_configure(
  dir = "_vcr",
  match_requests_on = c("method", "uri"),
  filter_request_headers = "Authorization"
)
vcr::setup_knitr(prefix = "")
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

One-page reference of the most-used cloudflarer calls. Every list
endpoint returns a data.frame (with `tbl_df` classes for tibble
users); pass `as_df = FALSE` for the raw nested list.

## Setup

```{r}
#| cassette: cheat-sitrep
# In ~/.Renviron
# CLOUDFLARE_API_TOKEN=...                  # recommended
# CLOUDFLARE_EMAIL=you@example.com          # OR (legacy)
# CLOUDFLARE_API_KEY=...

library(cloudflarer)
cf_sitrep()
```

## Discover what you can reach

```{r}
#| cassette: cheat-discover
cf_user()
cf_list_accounts()
cf_list_zones()
cf_list_zones(name = "example.com")
```

## Quick overview of a zone

```{r}
#| cassette: cheat-overview
zones <- cf_list_zones()
zone_id    <- zones$id[1]
account_id <- zones$account[[1]]$id

cf_zone_overview(zone_id, account_id = account_id)
```

`cf_zone_overview()` pulls traffic, cache ratio, DNS queries,
firewall events, and RUM top countries into one tidy bundle. Each
component is wrapped so a missing permission or Pro-only feature
yields `NULL` for that slot instead of failing the whole call.

## Traffic analytics

```{r}
#| cassette: cheat-traffic
cf_zone_requests(zone_id, Sys.Date() - 7, Sys.Date(), by = "day")
cf_zone_requests(zone_id, Sys.time() - 12 * 3600, Sys.time(), by = "hour")

cf_cache_ratio(zone_id, Sys.Date() - 7, Sys.Date())
cf_dns_queries(zone_id, Sys.Date() - 7, Sys.Date())

# Pro+ only:
cf_firewall_events_by_day(zone_id, Sys.Date() - 7, Sys.Date())
cf_firewall_events_top(
  zone_id, Sys.Date() - 7, Sys.Date(),
  dimension = "action", limit = 10
)
```

## Web Analytics (RUM)

```{r}
#| cassette: cheat-rum
sites <- cf_list_rum_sites(account_id)
site_tag <- sites$site_tag[1]

cf_rum_page_views(account_id, site_tag,
                  since = Sys.Date() - 30, until = Sys.Date())

cf_rum_top(account_id, site_tag,
           since = Sys.Date() - 30, until = Sys.Date(),
           dimension = "countryName", limit = 10)
```

## DNS records

```{r}
#| cassette: cheat-dns
cf_list_dns_records(zone_id, type = "A")

cf_create_dns_record(
  zone_id, type = "A", name = "blog",
  content = "192.0.2.5", proxied = TRUE
)

cf_update_dns_record(zone_id, "rec-1", content = "192.0.2.99")
cf_delete_dns_record(zone_id, "rec-1")
```

## Page Rules

```{r}
#| cassette: cheat-pagerules
cf_list_page_rules(zone_id)

cf_create_page_rule(
  zone_id,
  targets = list(cf_page_rule_target("*example.com/static/*")),
  actions = list(
    cf_page_rule_action("cache_level", "cache_everything"),
    cf_page_rule_action("edge_cache_ttl", 7200)
  )
)

cf_update_page_rule(zone_id, "rule-1", status = "disabled")
cf_delete_page_rule(zone_id, "rule-1")
```

## Cache purging

```{r}
#| cassette: cheat-cache
cf_purge_cache(zone_id, files = c(
  "https://example.com/index.html",
  "https://example.com/style.css"
))

cf_purge_cache(zone_id, prefixes = "example.com/blog")

cf_purge_cache(zone_id, purge_everything = TRUE)
```

## Zone settings

```{r}
#| cassette: cheat-settings
cf_get_zone_settings(zone_id)
cf_get_zone_setting(zone_id, "ssl")
```

## Email Routing

```{r}
#| cassette: cheat-email
cf_get_email_routing_settings(zone_id)
cf_list_email_routing_rules(zone_id)
cf_list_email_routing_addresses(account_id)
```

## Turnstile (CAPTCHA replacement)

```{r}
#| cassette: cheat-turnstile
cf_list_turnstile_widgets(account_id)

cf_create_turnstile_widget(
  account_id,
  name = "comment-form",
  domains = c("example.com", "www.example.com"),
  mode = "managed"
)
```

## Workers

```{r}
#| cassette: cheat-workers
cf_list_workers_scripts(account_id)
cf_workers_invocations(account_id, Sys.Date() - 7, Sys.Date())
cf_list_kv_namespaces(account_id)
```

## Pages, R2, Tunnels

```{r}
#| cassette: cheat-storage
cf_list_pages_projects(account_id)
cf_list_pages_deployments(account_id, "my-project")
cf_list_r2_buckets(account_id)
cf_list_tunnels(account_id)
```

## Firewall + Rulesets

```{r}
#| cassette: cheat-rulesets
cf_list_firewall_rules(zone_id)

# Modern rulesets surface:
cf_list_rulesets(zone_id)
cf_get_ruleset(zone_id, "rs-1")
cf_list_account_rulesets(account_id)
```

## Escape hatches

For anything cloudflarer does not wrap, drop down to the generics.
They handle auth and the envelope; you handle the path.

```{r}
#| cassette: cheat-escape
# Any REST endpoint: build -> pipe httr2 verbs -> perform -> unwrap
cf_request("user/tokens/verify") |>
  httr2::req_perform() |>
  cf_resp()
cf_request("zones/abc/dns_records") |>
  httr2::req_method("POST") |>
  httr2::req_body_json(list(type = "A", name = "x", content = "1.2.3.4")) |>
  httr2::req_perform() |>
  cf_resp()

# Paginated REST list (returns a raw list):
cf_request("accounts/abc/access/apps") |> cf_collect(per_page = 50)

# Any GraphQL Analytics query:
cf_graphql(
  "query Q($zoneTag: String!) {
    viewer { zones(filter: {zoneTag: $zoneTag}) { httpRequests1dGroups(
      limit: 7,
      filter: { date_geq: \"2026-05-14\", date_lt: \"2026-05-21\" }
    ) { dimensions { date } sum { requests } } } }
  }",
  zoneTag = zone_id
)
```

## Error handling

Every cloudflarer failure (HTTP error, envelope `success: false`,
GraphQL `errors[]`) raises a classed condition:

```{r}
#| cassette: cheat-error
tryCatch(
  cf_get_zone("does-not-exist"),
  cloudflarer_error = function(err) {
    message("Cloudflare said: ", conditionMessage(err))
    NULL
  }
)
```
